\chapter{Conclusion}\label{andfinally}
The last chapter of a well-structured report reviews what's been done and
mentions the main open questions.  It's the part a typical reader looks
at second, after the Introduction, and it should be just as appealing.
\begin{itemize}
    \item\verb+\documentclass[a4paper,twocolumn,10pt]{article}+
    gives an attractive alternative framework, for example.\par Or you
may prefer \verb+\documentclass{memoir}+ which has an excellent
manual \cite{MEM} that includes a general introduction to typography.
    \item Try to resist the temptation to make margins narrower
    and lines longer --- it may save a sheet or two of paper but it
    can make the text hard to read. Indeed, typesetting professionals
    quote a maximum of 66 characters per line as an ideal for easy reading
          \cite[Sec.~5.2.2]{NSS}.
    \item proof-read carefully --- not only to get the best from \LaTeX\
but also to polish grammar, spelling and punctuation \cite{ESL}.
App.~\ref{app:typo} alerts you to common pitfalls.
\end{itemize}.
\par
Top tip --- write what you think is the final version, then put it
away in a drawer and come back to it a week or so later. With fresh
eyes you'll see many potential improvements. This works for anything you
prepare, not just a project report. It needs forward planning of
course!
\section*{Acknowledgements}
\addcontentsline{toc}{chapter}{\numberline{}Acknowledgements}
Here's the place for thanks to anyone who particularly helped you.
Don't go too far OTT --- try to keep some dignity. This isn't the
Oscars.

